---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Reproducible Reprots

<!-- badges: start -->
<!-- badges: end -->

The goal of ReproducibleReprots is to go through an exercise where you can go through many phases that could be used for reproducible research:

## Preparation

For this we will need the bookdown, sf, tidyverse, rmarkdown, tinytex, and redoc packages, which you can install them by running the code

```{r, echo = T, eval = F}
install.packages(c("bookdown", "sf", "tidyverse", "rmarkdown", "tinytex", "plotly"))
```
 
And for redoc using the following one

```{r, echo = T, eval= F}
remotes::install_github("noamross/redoc")
```

Once you have installed all those packages it is highly recomended that you run the following code:

```{r, echo = T, eval= F}
tinytex::install_tinytex()
```

This will install a small latex generator in your r environment, which will result in the option to render PDF reports

## Motivation

In this workshop we will see how you can use rmarkdown to generate reproducible documents that can become the [webpage of a project](https://danish-flora-and-vegetation.github.io/), including interactive [plots and documents](https://danish-flora-and-vegetation.github.io/MapAndnmds/map.html). Presentations with [interactive elements](https://rpubs.com/derek_corcoran/MolsRewild) and even fully rendered manuscripts. 

## Activities

1. Clone a repository (this one).
2. Generate a report with bookdown, using the template in this repo.
3. Add bibliography (.bib file) to manage your references.
4. Add a couple of plots and use [crossreferences](https://bookdown.org/yihui/rmarkdown-cookbook/cross-ref.html) for it.
5. Generate a pdf report.
6. Generate a .docx report, send it to someone else to edit it and check the control changes using the redoc package.
7. if we have time, we can add a ioslides presentation

## Extra demos

1. Generation of latex documents and further editing with overleaf
